---
title: "WB - LRSP Monitoring survey - 2025"
author: ""
date: "[April 08, 2025 | 01:00 AM]"
output: 
  flexdashboard::flex_dashboard:
    
    
    orientation: row
    vertical_layout: fill
    logo: logo.png
runtime: shiny

---

```{r setup, include=FALSE}
library(flexdashboard)
library(haven)
library(plyr)
library(tidyverse)
library(dplyr)
library(lubridate)
library(highcharter)
library(plotly)
library(DT)
library(stringr)
library(ggplot2)
library(viridis)
library(hrbrthemes)
library(reshape2)
library(ggalt)
library(treemap)
library(networkD3)
library(reshape2)
library(fmsb)
library(leaflet)

```

```{r}
# Load required libraries
library(haven)
library(dplyr)

# Read the Stata .dta file
data_mo <- read_dta("D:/Projects/LRSP/LRSP-dashboard-main/LRSP/_LRSP_Monitoring_Survey_Final.dta")

# Convert all labelled variables to factors
data_mo <- data_mo %>% mutate(across(everything(), ~ as_factor(.)))

```

```{r}
# Load required libraries
library(haven)
library(dplyr)

# Read the Stata .dta file
data_hh <- read_dta("D:/Projects/LRSP/LRSP-dashboard-main/LRSP/_LRSP_HH_Monitoring_Survey_Final.dta")

# Convert all labelled variables to factors
data_hh <- data_hh %>% mutate(across(everything(), ~ as_factor(.)))

```

HOME
=====================================
Row
-----------------------------------------------------------------------


### TOTAL SYNCED LRSP MONITORING SURVEY

```{r, echo=FALSE, results='asis'}
library(haven)
library(dplyr)

# Load and prepare data
data_mo <- read_dta("D:/Projects/LRSP/LRSP-dashboard-main/LRSP/_LRSP_Monitoring_Survey_Final.dta")
data_mo <- data_mo %>% mutate(across(everything(), ~ as_factor(.)))
total_interview <- nrow(data_mo)

# Create a styled value box with a simple hover effect
cat(sprintf('
<style>
.hover-box {
  background-color: #007bff;
  color: white;
  padding: 30px;
  border-radius: 12px;
  text-align: center;
  width: 800px;
  margin: 30px auto;
  transition: transform 0.3s ease;
  font-family: Arial, sans-serif;
}
.hover-box:hover {
  transform: scale(1.05);
}
.hover-box .title {
  font-size: 20px;
  margin-bottom: 10px;
  font-weight: bold;
}
.hover-box .value {
  font-size: 48px;
}
</style>

<div class="hover-box">
  <div class="title">Total LRSP synced Interviews</div>
  <div class="value">%s</div>
</div>
', total_interview))
```


### TOTAL SYNCED HOUSEHOLD SURVEY

```{r, echo=FALSE, results='asis'}
library(haven)
library(dplyr)

# Load and prepare data

total_interview <- nrow(data_hh)

# Create a styled value box with a simple hover effect
cat(sprintf('
<style>
.hover-box {
  background-color: #007bff;
  color: white;
  padding: 30px;
  border-radius: 12px;
  text-align: center;
  width: 800px;
  margin: 30px auto;
  transition: transform 0.3s ease;
  font-family: Arial, sans-serif;
}
.hover-box:hover {
  transform: scale(1.05);
}
.hover-box .title {
  font-size: 20px;
  margin-bottom: 10px;
  font-weight: bold;
}
.hover-box .value {
  font-size: 48px;
}
</style>

<div class="hover-box">
  <div class="title">Total Household synced Interviews</div>
  <div class="value">%s</div>
</div>
', total_interview))
```

Row
-----------------------------------------------------------------------


### NO. OF HH SURVEY INTERVIEWS BY KEBELE {data-width=300}

```{r}
library(dplyr)
library(highcharter)

# ==== Kebele Chart with Fullscreen on Click ====
kebele_data <- data_hh %>%
  count(kebele, name = "Total") %>%
  arrange(desc(Total))

avg_count <- mean(kebele_data$Total)

hchart(kebele_data, "bar", hcaes(x = kebele, y = Total),
       color = color_stops(n = nrow(kebele_data),
                           colors = c("#F72585", "#B5179E", "#7209B7", "#3A0CA3", "#4361EE", "#4CC9F0"))
) %>%
  hc_title(text = "ðŸŒ Interview Count by Kebele") %>%
  hc_subtitle(text = paste("Average Interviews per Kebele:", round(avg_count, 1))) %>%
  hc_xAxis(title = list(text = "Kebele")) %>%
  hc_yAxis(
    title = list(text = "Number of Household Interviews"),
    plotLines = list(
      list(
        value = avg_count,
        color = "#FF8C00",
        width = 2,
        dashStyle = "Dash",
        label = list(text = paste("Average: ", round(avg_count, 1)),
                     style = list(color = "#FF8C00", fontWeight = "bold"))
      )
    )
  ) %>%
  hc_plotOptions(bar = list(
    dataLabels = list(enabled = TRUE, format = '{point.y}'),
    borderRadius = 5,
    groupPadding = 0.1,
    pointPadding = 0.1,
    point = list(
      events = list(
        click = JS("function () {
          if (this.series.chart.fullscreen) {
            this.series.chart.fullscreen.toggle();
          }
        }")
      )
    )
  )) %>%
  hc_tooltip(
    backgroundColor = "#ffffff",
    borderColor = "#ccc",
    pointFormat = "<b>{point.kebele}</b><br>Interviews: <b>{point.Total}</b>"
  ) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  ) %>%
  hc_exporting(enabled = TRUE)


# ==== Woreda Chart with Fullscreen on Click ====
data_woreda <- data_hh %>%
  filter(!is.na(woreda)) %>%
  count(woreda, name = "Total") %>%
  arrange(desc(Total))

hchart(
  data_woreda,
  "bar",
  hcaes(x = woreda, y = Total),
  color = color_stops(
    n = nrow(data_woreda),
    colors = c("#F65A83", "#FF1E00", "#21E1E1", "#28a745", "#224B0C")
  )
) %>%
  hc_title(text = "ðŸ“Š Total Interviews by Woreda") %>%
  hc_subtitle(text = "Bar chart showing total interview count per woreda") %>%
  hc_xAxis(title = list(text = "Woreda")) %>%
  hc_yAxis(title = list(text = "Number of Interviews")) %>%
  hc_tooltip(
    pointFormat = "<b>{point.woreda}</b>: <b>{point.Total}</b> interviews"
  ) %>%
  hc_plotOptions(bar = list(
    dataLabels = list(enabled = TRUE),
    borderRadius = 3,
    point = list(
      events = list(
        click = JS("function () {
          if (this.series.chart.fullscreen) {
            this.series.chart.fullscreen.toggle();
          }
        }")
      )
    )
  )) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  ) %>%
  hc_exporting(enabled = TRUE)


```

### NO. OF HH SURVEY INTERVIEWS BY WOREDA {data-width=300}

```{r}
library(dplyr)
library(highcharter)

# Step 1: Count total interviews by woreda
data_woreda <- data_hh %>%
  filter(!is.na(woreda)) %>%
  count(woreda, name = "Total") %>%
  arrange(desc(Total))

# Step 2: Plot bar chart
hchart(
  data_woreda,
  "bar",
  hcaes(x = woreda, y = Total),
  color = color_stops(
    n = 5,
    colors = c("#F65A83", "#FF1E00", "#21E1E1", "#28a745", "#224B0C")
  )
) %>%
  hc_title(text = "ðŸ“Š Total Interviews by Woreda") %>%
  hc_subtitle(text = "Bar chart showing total interview count per woreda") %>%
  hc_xAxis(title = list(text = "Woreda")) %>%
  hc_yAxis(title = list(text = "Number of Interviews")) %>%
  hc_tooltip(
    pointFormat = "<b>{point.woreda}</b>: <b>{point.Total}</b> interviews"
  ) %>%
  hc_plotOptions(bar = list(
    dataLabels = list(enabled = TRUE),
    borderRadius = 3
  )) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  )

```

### NO. OF LRSP Monitoring SURVEY INTERVIEWS BY KEBELE {data-width=300}

```{r}
library(dplyr)
library(highcharter)

# ==== Kebele Chart with Fullscreen on Click ====
kebele_data <- data_mo %>%
  count(kebele, name = "Total") %>%
  arrange(desc(Total))

avg_count <- mean(kebele_data$Total)

hchart(kebele_data, "bar", hcaes(x = kebele, y = Total),
       color = color_stops(n = nrow(kebele_data),
                           colors = c("#F72585", "#B5179E", "#7209B7", "#3A0CA3", "#4361EE", "#4CC9F0"))
) %>%
  hc_title(text = "ðŸŒ Interview Count by Kebele") %>%
  hc_subtitle(text = paste("Average Interviews per Kebele:", round(avg_count, 1))) %>%
  hc_xAxis(title = list(text = "Kebele")) %>%
  hc_yAxis(
    title = list(text = "Number of LRSP Monitoring Interviews"),
    plotLines = list(
      list(
        value = avg_count,
        color = "#FF8C00",
        width = 2,
        dashStyle = "Dash",
        label = list(text = paste("Average: ", round(avg_count, 1)),
                     style = list(color = "#FF8C00", fontWeight = "bold"))
      )
    )
  ) %>%
  hc_plotOptions(bar = list(
    dataLabels = list(enabled = TRUE, format = '{point.y}'),
    borderRadius = 5,
    groupPadding = 0.1,
    pointPadding = 0.1,
    point = list(
      events = list(
        click = JS("function () {
          if (this.series.chart.fullscreen) {
            this.series.chart.fullscreen.toggle();
          }
        }")
      )
    )
  )) %>%
  hc_tooltip(
    backgroundColor = "#ffffff",
    borderColor = "#ccc",
    pointFormat = "<b>{point.kebele}</b><br>Interviews: <b>{point.Total}</b>"
  ) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  ) %>%
  hc_exporting(enabled = TRUE)


# ==== Woreda Chart with Fullscreen on Click ====
data_woreda <- data_hh %>%
  filter(!is.na(woreda)) %>%
  count(woreda, name = "Total") %>%
  arrange(desc(Total))

hchart(
  data_woreda,
  "bar",
  hcaes(x = woreda, y = Total),
  color = color_stops(
    n = nrow(data_woreda),
    colors = c("#F65A83", "#FF1E00", "#21E1E1", "#28a745", "#224B0C")
  )
) %>%
  hc_title(text = "ðŸ“Š Total Interviews by Woreda") %>%
  hc_subtitle(text = "Bar chart showing total interview count per woreda") %>%
  hc_xAxis(title = list(text = "Woreda")) %>%
  hc_yAxis(title = list(text = "Number of Interviews")) %>%
  hc_tooltip(
    pointFormat = "<b>{point.woreda}</b>: <b>{point.Total}</b> interviews"
  ) %>%
  hc_plotOptions(bar = list(
    dataLabels = list(enabled = TRUE),
    borderRadius = 3,
    point = list(
      events = list(
        click = JS("function () {
          if (this.series.chart.fullscreen) {
            this.series.chart.fullscreen.toggle();
          }
        }")
      )
    )
  )) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  ) %>%
  hc_exporting(enabled = TRUE)


```

### NO. OF LRSP Monitoring SURVEY INTERVIEWS BY WOREDA {data-width=300}

```{r}
library(dplyr)
library(highcharter)

# Step 1: Count total interviews by woreda
data_woreda <- data_mo %>%
  filter(!is.na(woreda)) %>%
  count(woreda, name = "Total") %>%
  arrange(desc(Total))

# Step 2: Plot bar chart
hchart(
  data_woreda,
  "bar",
  hcaes(x = woreda, y = Total),
  color = color_stops(
    n = 5,
    colors = c("#F65A83", "#FF1E00", "#21E1E1", "#28a745", "#224B0C")
  )
) %>%
  hc_title(text = "ðŸ“Š Total Interviews LRSP by Woreda") %>%
  hc_subtitle(text = "Bar chart showing total interview count per woreda") %>%
  hc_xAxis(title = list(text = "Woreda")) %>%
  hc_yAxis(title = list(text = "Number of Interviews")) %>%
  hc_tooltip(
    pointFormat = "<b>{point.woreda}</b>: <b>{point.Total}</b> interviews"
  ) %>%
  hc_plotOptions(bar = list(
    dataLabels = list(enabled = TRUE),
    borderRadius = 3
  )) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  )

```
Column 
-----------------------------------------------------------------------
### NO. OF LRSP MONITORING SURVEY INTERVIEWS DONE BY DATE {data-width=400}

```{r }
library(dplyr)
library(tidyr)
library(lubridate)
library(highcharter)

# Prepare data
data_date <- data_mo %>%
  mutate(date = as.Date(date)) %>%
  filter(!is.na(date)) %>%
  count(date, name = "Total") %>%
  arrange(date)

# Fill missing dates
date_full <- data.frame(date = seq.Date(min(data_date$date), max(data_date$date), by = "day"))

data_clean <- date_full %>%
  left_join(data_date, by = "date") %>%
  replace_na(list(Total = 0))

# Render the chart
hchart(
  data_clean,
  type = "line",
  hcaes(x = date, y = Total),
  color = "#28a745"
) %>%
  hc_title(text = "ðŸ“ˆ Daily Interview Count") %>%
  hc_subtitle(text = "LRSP MONITORING SURVEY INTERVIEWS DONE BY DATE") %>%
  hc_xAxis(
    type = "datetime",
    title = list(text = "Date"),
    labels = list(format = "{value:%b %d}")
  ) %>%
  hc_yAxis(
    title = list(text = "Number of Interviews"),
    min = 0
  ) %>%
  hc_tooltip(
    xDateFormat = "%A, %b %d",
    pointFormat = "<b>{point.Total}</b> interviews"
  ) %>%
  hc_plotOptions(
    series = list(
      cursor = "pointer",
      point = list(
        events = list(
          click = JS("
            function () {
              if (this.series.chart.fullscreen) {
                this.series.chart.fullscreen.toggle();
              }
            }
          ")
        )
      )
    )
  ) %>%
  hc_chart(
    backgroundColor = "#f7fcf8",
    style = list(fontFamily = "Inter, sans-serif")
  ) %>%
  hc_exporting(
    enabled = TRUE,
    buttons = list(
      contextButton = list(enabled = FALSE)  # Removes export menu (burger)
    )
  )


```

### NO. OF LRSP HH SURVEY INTERVIEWS DONE BY DATE {data-width=400}
```{r}
# Load required libraries
library(dplyr)
library(tidyr)
library(lubridate)
library(highcharter)

# Step 1: Clean and prepare date-wise data
data_date <- data_hh %>%
  mutate(date = as.Date(date)) %>%          # Convert to Date type
  filter(!is.na(date)) %>%                  # Remove NAs
  count(date, name = "Total") %>%           # Count interviews per date
  arrange(date)

# Step 2: Create full sequence of dates (fills missing days with 0s)
start_date <- min(data_date$date, na.rm = TRUE)
end_date   <- max(data_date$date, na.rm = TRUE)

date_full <- data.frame(date = seq.Date(start_date, end_date, by = "day"))

# Step 3: Merge with actual data and fill in missing days
data_clean <- date_full %>%
  left_join(data_date, by = "date") %>%
  replace_na(list(Total = 0))

# Step 4: Plot the clean green line chart
hchart(
  data_clean,
  type = "line",
  hcaes(x = date, y = Total),
  color = "#28a745"  # Clean green line
) %>%
  hc_title(text = "ðŸ“ˆ Daily Interview Count") %>%
  hc_subtitle(text = "LRSP HH SURVEY INTERVIEWS DONE BY DATE") %>%
  hc_xAxis(
    type = "datetime",
    title = list(text = "Date"),
    labels = list(format = "{value:%b %d}"),
    lineColor = "#ccc",
    gridLineWidth = 0.5
  ) %>%
  hc_yAxis(
    title = list(text = "Number of Interviews"),
    min = 0,
    gridLineDashStyle = "ShortDash"
  ) %>%
  hc_tooltip(
    xDateFormat = "%A, %b %d",
    pointFormat = "<b>{point.Total}</b> interviews",
    backgroundColor = "#f0fff0",
    borderColor = "#28a745"
  ) %>%
  hc_plotOptions(line = list(
    lineWidth = 4,
    marker = list(
      enabled = TRUE,
      radius = 4,
      fillColor = "#ffffff",
      lineColor = "#28a745",
      lineWidth = 2
    ),
    dataLabels = list(enabled = FALSE)
  )) %>%
  hc_chart(
    backgroundColor = "#f7fcf8",
    style = list(fontFamily = "Inter, sans-serif")
  )

```


VISIT REPORT LRSP
=====================================

Row
-----------------------------------------------------------------------

### LRSP MONITORING SURVEY INTERVIEWS BY VISIT {data-width=300}


```{r}
library(dplyr)
library(highcharter)

# Define visit order
visit_levels <- c("First - Third Visit", "Second - Third Visit", 
                  "Fourth Visit", "Fifth Visit", "Sixth Visit", "Seventh Visit")

# Prepare data
visit_summary <- data_mo %>%
  filter(!is.na(visit)) %>%
  mutate(visit = factor(visit, levels = visit_levels)) %>%
  count(visit, name = "Total") %>%
  arrange(visit)

# Create bar chart with zoom-out animation effect
hchart(
  visit_summary,
  type = "column",
  hcaes(x = visit, y = Total)
) %>%
  hc_title(text = "ðŸ“Š Number of Interviews by Visit") %>%
  hc_subtitle(text = "Bar chart showing count of interviews per visit round of LRSP Monitoring Survey") %>%
  hc_xAxis(title = list(text = "Visit Type")) %>%
  hc_yAxis(title = list(text = "Number of Interviews")) %>%
  hc_tooltip(pointFormat = "<b>{point.x}</b>: {point.y} interviews") %>%
  hc_plotOptions(
    column = list(
      colorByPoint = TRUE,
      dataLabels = list(
        enabled = TRUE,
        format = '{point.y}',
        style = list(fontWeight = "bold")
      ),
      animation = list(
        duration = 1200,
        easing = "easeOutBounce"  # Simulates a bounce-style zoom-out
      )
    )
  ) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif"),
    animation = list(
      duration = 1200
    )
  ) %>%
  hc_colors(c("#28a745", "#FF6B6B", "#1E90FF", "#FFC107", "#8E44AD", "#00B894"))

```
### LRSP MONITORING SURVEY INTERVIEWS BY VISIT {data-width=300}

```{r}
library(dplyr)
library(highcharter)

# Prepare data: count interviews by 'visit'
visit_summary <- data_mo %>%
  filter(!is.na(visit)) %>%
  count(visit, name = "Total") %>%
  arrange(desc(Total))

# Create donut chart
hchart(
  visit_summary,
  "pie",
  hcaes(name = visit, y = Total)
) %>%
  hc_title(text = " Interviews by Visit Round") %>%
  hc_subtitle(text = "Donut chart showing interview counts per visit round of LRSP Monitoring Survey") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>: <b>{point.y}</b> interviews<br>({point.percentage:.1f}%)") %>%
  hc_plotOptions(
    pie = list(
      innerSize = '60%',  # This creates the donut hole
      allowPointSelect = TRUE,
      cursor = "pointer",
      dataLabels = list(
        enabled = TRUE,
        format = "<b>{point.name}</b>: {point.percentage:.1f} %",
        distance = -30,
        style = list(color = "white", fontWeight = "bold")
      ),
      showInLegend = TRUE
    )
  ) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  ) %>%
  hc_colors(c("#28a745", "#FF6B6B", "#1E90FF", "#FFC107", "#8E44AD", "#00B894"))

```


Column 
-----------------------------------------------------------------------

### NO. OF LRSP INTERVIEWS DONE BY KEBELE {data-width=400}

```{r}
library(dplyr)
library(highcharter)

# Summarize interview counts by kebele
kebele_summary <- data_mo %>%
  filter(!is.na(kebele)) %>%
  count(kebele, name = "Total") %>%
  arrange(desc(Total))

# Create pie chart
hchart(
  kebele_summary,
  "pie",
  hcaes(name = kebele, y = Total)
) %>%
  hc_title(text = "ðŸ¥§ Interview Distribution by Kebele") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>: <b>{point.y}</b> interviews<br>({point.percentage:.1f}%)") %>%
  hc_plotOptions(
    pie = list(
      allowPointSelect = TRUE,
      cursor = "pointer",
      dataLabels = list(
        enabled = TRUE,
        format = "<b>{point.name}</b>: {point.percentage:.1f} %"
      )
    )
  ) %>%
  hc_chart(backgroundColor = "#f9f9f9")

```


### NO. OF LRSP INTERVIEWS DONE BY WOREDA {data-width=400}

```{r}
library(dplyr)
library(highcharter)

# Summarize interview counts by woreda
woreda_summary <- data_mo %>%
  filter(!is.na(woreda)) %>%
  count(woreda, name = "Total") %>%
  arrange(desc(Total))

# Create pie chart
hchart(
  woreda_summary,
  "pie",
  hcaes(name = woreda, y = Total)
) %>%
  hc_title(text = " Interview Distribution by Woreda") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>: <b>{point.y}</b> interviews<br>({point.percentage:.1f}%)") %>%
  hc_plotOptions(
    pie = list(
      allowPointSelect = TRUE,
      cursor = "pointer",
      dataLabels = list(
        enabled = TRUE,
        format = "<b>{point.name}</b>: {point.percentage:.1f} %"
      )
    )
  ) %>%
  hc_chart(backgroundColor = "#f9f9f9")

```

VISIT REPORT HH
=====================================

Row
-----------------------------------------------------------------------

### LRSP HH SURVEY INTERVIEWS BY VISIT {data-width=300}


```{r}
library(dplyr)
library(highcharter)

# Group and count interviews by 'visit'
visit_summary <- data_hh %>%
  filter(!is.na(visit)) %>%
  count(visit, name = "Total") %>%
  arrange(desc(Total))

# Plot bar chart
hchart(
  visit_summary,
  "column",
  hcaes(x = visit, y = Total),
  color = "#28a745"  # Green color for style
) %>%
  hc_title(text = "ðŸ“‹ Number of Interviews by Visit") %>%
  hc_subtitle(text = "Bar chart showing count of interviews per visit round of LRSP Household Survey") %>%
  hc_xAxis(title = list(text = "Visit Type")) %>%
  hc_yAxis(title = list(text = "Number of Interviews"), min = 0) %>%
  hc_tooltip(pointFormat = "<b>{point.visit}</b>: <b>{point.Total}</b> interviews") %>%
  hc_plotOptions(column = list(
    dataLabels = list(enabled = TRUE),
    borderRadius = 3
  )) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  )

```
### LRSP HH SURVEY INTERVIEWS BY VISIT {data-width=300}

```{r}
library(dplyr)
library(highcharter)

# Prepare data: count interviews by 'visit'
visit_summary <- data_hh %>%
  filter(!is.na(visit)) %>%
  count(visit, name = "Total") %>%
  arrange(desc(Total))

# Create donut chart
hchart(
  visit_summary,
  "pie",
  hcaes(name = visit, y = Total)
) %>%
  hc_title(text = " Interviews by Visit Round") %>%
  hc_subtitle(text = "Donut chart showing interview counts per visit round of LRSP Household Survey") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>: <b>{point.y}</b> interviews<br>({point.percentage:.1f}%)") %>%
  hc_plotOptions(
    pie = list(
      innerSize = '60%',  # Donut hole
      allowPointSelect = TRUE,
      cursor = "pointer",
      dataLabels = list(
        enabled = TRUE,
        format = "<b>{point.name}</b>: {point.percentage:.1f} %",
        distance = -30,
        style = list(color = "white", fontWeight = "bold")
      ),
      showInLegend = TRUE
    )
  ) %>%
  hc_chart(
    backgroundColor = "#f5f7fa",
    style = list(fontFamily = "Inter, sans-serif")
  ) %>%
  hc_colors(c("#28a745", "#FF6B6B", "#1E90FF", "#FFC107", "#8E44AD", "#00B894"))

```


Column 
-----------------------------------------------------------------------

### NO. OF HH INTERVIEWS DONE BY KEBELE {data-width=400}

```{r}
library(dplyr)
library(highcharter)

# Summarize interview counts by kebele
kebele_summary <- data_hh %>%
  filter(!is.na(kebele)) %>%
  count(kebele, name = "Total") %>%
  arrange(desc(Total))

# Create pie chart
hchart(
  kebele_summary,
  "pie",
  hcaes(name = kebele, y = Total)
) %>%
  hc_title(text = " Interview Distribution by Kebele") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>: <b>{point.y}</b> interviews<br>({point.percentage:.1f}%)") %>%
  hc_plotOptions(
    pie = list(
      allowPointSelect = TRUE,
      cursor = "pointer",
      dataLabels = list(
        enabled = TRUE,
        format = "<b>{point.name}</b>: {point.percentage:.1f} %"
      )
    )
  ) %>%
  hc_chart(backgroundColor = "#f9f9f9")

```


### NO. OF HH INTERVIEWS DONE BY WOREDA {data-width=400}

```{r}
library(dplyr)
library(highcharter)

# Summarize interview counts by woreda
woreda_summary <- data_hh %>%
  filter(!is.na(woreda)) %>%
  count(woreda, name = "Total") %>%
  arrange(desc(Total))

# Create pie chart
hchart(
  woreda_summary,
  "pie",
  hcaes(name = woreda, y = Total)
) %>%
  hc_title(text = " Interview Distribution by Woreda") %>%
  hc_tooltip(pointFormat = "<b>{point.name}</b>: <b>{point.y}</b> interviews<br>({point.percentage:.1f}%)") %>%
  hc_plotOptions(
    pie = list(
      allowPointSelect = TRUE,
      cursor = "pointer",
      dataLabels = list(
        enabled = TRUE,
        format = "<b>{point.name}</b>: {point.percentage:.1f} %"
      )
    )
  ) %>%
  hc_chart(backgroundColor = "#f9f9f9")

```


Test
=====================================

Row
-----------------------------------------------------------------------

### LRSP HH SURVEY INTERVIEWS BY VISIT {data-width=300}

```{r}


```

